Supplementary material

### 2020-06-30 Manuscript/ms.tex
Cleaning up notation and typos

We specified the differential equations governing the human population as:
\begin{align} 
\frac{dS}{dt} &= bN - bS - \lambda \frac{V_{I}}{N} S + \delta R\\
\frac{dE}{dt} &= \lambda \frac{V_{I}}{N} S - (\rho + b)E\\
\frac{dI}{dt} &= \rho E - (\gamma + b)I\\
\frac{dR}{dt} &= \gamma I - (\delta + b)R
\end{align}
while the equations governing the mosquito (vector) population are:
\begin{align}
\frac{dV_N}{dt} & = r(t) V_N - \phi_q \tau(t) V_N \\
\frac{dV_{E1}}{dt} &= \lambda \frac{I}{N} V_S - (\nu\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E1}\\
\frac{dV_{E2}}{dt} &= \nu\rho_{v}(t) V_{E1} - (\nu\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E2}\\
\frac{dV_{E3}}{dt} &= \nu\rho_{v}(t) V_{E2}  - (\nu\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E3}\\
\frac{dV_{E4}}{dt} &= \nu\rho_{v}(t) V_{E3}  - (\nu\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E4}\\
\frac{dV_I}{dt} &= \nu\rho_{v}(t) V_{E4} - (d(t) + \phi_q \tau(t)) V_I\\
\frac{dV_C}{dt} & = \phi_q \tau(t) V_N\\
V_S &= V_N - V_E - V_I.
\end{align}

@@

\begin{table}[!ht]
\label{parameters}
\begin{adjustwidth}{-2.25in}{0in} 
\begin{center}
\caption{Model parameters and their values.  Parameters above the rule are fixed, while parameters below the rule are random.  The values in parentheses after the posterior means give the 80$\%$ credible interval. See Supplemental Material for a full description of all prior distributions.}
\begin{tabular}{lp{6cm}lll}
Parameter & Description & Prior mean & Posterior mean & Citation\\
\hline
$N$ & Human population size in Vit\'oria, Brazil & 327801 & & \cite{vitpop} \\
$1/d$ & Human life-span & 76 years & &\cite{vitlong} \\
$\lambda$ & Transmission rate & 4.87 week$^{-1}$ & & \cite{Scott2000}\\
$1/\rho_{v}(t)$ & Extrinsic incubation period & $\exp\left(7.9 - 0.21 T(t) \right)$ days & & \cite{Chan2012}\\
$V_{E0}$ & Initial exposed mosquitoes &  0 & &\\
$V_{I0}$ & Initial infectious mosquitoes & 0 & &\\
\hline
$d_0$ & Baseline mosquito mortality rate & 1.47 week$^{-1}$ & 0.88 (0.7, 1.1) &  \cite{Brady2013} \\
$1/\rho$ & Latent period in host & 0.87 weeks  & 1.72 (1.2, 2.3) &  \cite{Chan2012}\\
$\gamma$ & Rate of loss of infectiousness & 3.5 week$^{-1}$ & 3.6 (3.2, 4.1) & \cite{Nguyet2013}\\
$1/\delta$ & Period of cross-immunity & 97 weeks &  114 (72, 160) & \cite{Reich2013}\\
$\sigma_r$ & Standard deviation of mosquito growth rate forcing & $0^*$ & 0.013 (0.01, 0.02) &\\
$\sigma_{\nu}$ & Standard deviation of mosquito mortality rate forcing & $0^*$ & 0.0005 (0.0004, 0.0008) & \\
$S_0$ & Proportion initially susceptible & 0.4 & 0.42 (0.28, 0.57)& \cite{Cardoso2011a} \\
$E_0$ & Number initially exposed & $100$ & 148 (104, 196) & \\
$I_0$ & Number initially infectious & $60$ & 79 (45, 116) &\\
$r_0$ & Initial mosquito population growth rate & 0 & 0.008 (-0.01, 0.02) &\\
$\nu_0$ & Initial unconstrained mosquito mortality rate & 0 & -0.16 (-0.4, 0.08) &\\
$V_{N0}$ & Initial mosquito population size & $2N$ & $1.5N$ $(1.1N, 1.9N)$ &\\
$\phi_y$ & Reporting probability & 0.083 & 0.14  (0.1, 0.18) &\cite{Silva2016}\\
$\log(\phi_q)$ & Log per-trap mosquito capture rate & $-13$  & -13.2 (-13.6, -13)  &\\
$\eta_y$ & Overdispersion of case reports & $0^*$ & 0.12 (0.1, 0.13) &\\
$\eta_q$ & Overdispersion of mosquito trap counts & $0^*$ & 0.14 (0.12, 0.16)&\\
\end{tabular}
\end{center}
\end{adjustwidth}
$^*$ indicates prior mode, rather than mean.
\end{table}

@@

The estimated weekly mosquito mortality rate varied seasonally, with generally high mortality early in the year and low mortality in August to October (Figure \ref{timeseries}).
This seasonal trend broadly tracked seasonal variation in temperature (Figure \ref{mortality}, posterior mean correlation coefficient of 0.64) and mosquito trap counts (Figure \ref{timeseries}, though the shape of the annual trajectory differed from year to year.
The posterior distribution of the baseline mortality rate ($d_0$) had a mean of 0.88/week, roughly $60\%$ of the prior mean.
The marginal posterior means of the $\epsilon_{\nu t}$ forcing the mosquito mortality process exhibited a higher-frequency periodic oscillation (Supplementary Figure 1), although the marginal posterior distribution of each $\epsilon_{\nu t}$ overlapped zero.
In addition, the standard deviation of the mortality forcing terms was small relative to the weak prior ($E(\sigma_{\nu}|\mathbf{y}) = 0.01$, Supplemental Figure 2).

>>>>

We specified the differential equations governing the human population as:
\begin{align} 
\frac{dS}{dt} &= bN - bS - \lambda \frac{V_{I}}{N} S + \delta R\\
\frac{dE}{dt} &= \lambda \frac{V_{I}}{N} S - (\rho + b)E\\
\frac{dI}{dt} &= \rho E - (\gamma + b)I\\
\frac{dR}{dt} &= \gamma I - (\delta + b)R
\end{align}
while the equations governing the mosquito (vector) population are:
\begin{align}
\frac{dV_N}{dt} & = r(t) V_N - \phi_q \tau(t) V_N \\
\frac{dV_{E1}}{dt} &= \lambda \frac{I}{N} V_S - (4\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E1}\\
\frac{dV_{E2}}{dt} &= 4\rho_{v}(t) V_{E1} - (4\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E2}\\
\frac{dV_{E3}}{dt} &= 4\rho_{v}(t) V_{E2}  - (4\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E3}\\
\frac{dV_{E4}}{dt} &= 4\rho_{v}(t) V_{E3}  - (4\rho_{v}(t) + d(t) + \phi_q \tau(t))V_{E4}\\
\frac{dV_I}{dt} &= 4\rho_{v}(t) V_{E4} - (d(t) + \phi_q \tau(t)) V_I\\
\frac{dV_C}{dt} & = \phi_q \tau(t) V_N\\
V_S &= V_N - V_E - V_I.
\end{align}

@@

\begin{table}[!ht]
\label{parameters}
\begin{adjustwidth}{-2.25in}{0in} 
\begin{center}
\caption{Model parameters and their values.  Parameters above the rule are fixed, while parameters below the rule are random.  The values in parentheses after the posterior means give the 80$\%$ credible interval. See Supplemental Material for a full description of all prior distributions.}
\begin{tabular}{lp{6cm}lll}
Parameter & Description & Prior mean & Posterior mean & Citation\\
\hline
$N$ & Human population size in Vit\'oria, Brazil & 327801 & & \cite{vitpop} \\
$1/d$ & Human life-span & 76 years & &\cite{vitlong} \\
$\lambda$ & Transmission rate & 4.87 week$^{-1}$ & & \cite{Scott2000}\\
$1/\rho_{v}(t)$ & Extrinsic incubation period & $\frac{1}{7}\exp\left(7.9 - 0.21 T(t) \right)$ weeks & & \cite{Chan2012}\\
$V_{E0}$ & Initial exposed mosquitoes &  0 & &\\
$V_{I0}$ & Initial infectious mosquitoes & 0 & &\\
\hline
$d_0$ & Baseline mosquito mortality rate & 1.47 week$^{-1}$ & 0.88 (0.7, 1.1) &  \cite{Brady2013} \\
$1/\rho$ & Latent period in host & 0.87 weeks  & 1.72 (1.2, 2.3) &  \cite{Chan2012}\\
$\gamma$ & Rate of loss of infectiousness & 3.5 week$^{-1}$ & 3.6 (3.2, 4.1) & \cite{Nguyet2013}\\
$1/\delta$ & Period of cross-immunity & 97 weeks &  114 (72, 160) & \cite{Reich2013}\\
$\sigma_r$ & Standard deviation of mosquito growth rate forcing & $0^*$ & 0.013 (0.01, 0.02) &\\
$\sigma_{\nu}$ & Standard deviation of mosquito mortality rate forcing & $0^*$ & 0.0005 (0.0004, 0.0008) & \\
$S_0$ & Proportion initially susceptible & 0.4 & 0.42 (0.28, 0.57)& \cite{Cardoso2011a} \\
$E_0$ & Number initially exposed & $100$ & 148 (104, 196) & \\
$I_0$ & Number initially infectious & $60$ & 79 (45, 116) &\\
$r_0$ & Initial mosquito population growth rate & 0 & 0.008 (-0.01, 0.02) &\\
$\nu_0$ & Initial unconstrained mosquito mortality rate & 0 & -0.16 (-0.4, 0.08) &\\
$V_{N0}$ & Initial mosquito population size & $2N$ & $1.5N$ $(1.1N, 1.9N)$ &\\
$\phi_y$ & Reporting probability & 0.083 & 0.14  (0.1, 0.18) &\cite{Silva2016}\\
$\log(\phi_q)$ & Log per-trap mosquito capture rate & $-13$  & -13.2 (-13.6, -13)  &\\
$\eta_y$ & Overdispersion of case reports & $0^*$ & 0.12 (0.1, 0.13) &\\
$\eta_q$ & Overdispersion of mosquito trap counts & $0^*$ & 0.14 (0.12, 0.16)&\\
\end{tabular}
\end{center}
\end{adjustwidth}
$^*$ indicates prior mode, rather than mean.
\end{table}

@@

The estimated weekly mosquito mortality rate varied seasonally, with generally high mortality early in the year and low mortality in August to October (Figure \ref{timeseries}).
This seasonal trend broadly tracked seasonal variation in temperature (Figure \ref{mortality}, correlation coefficient of 0.64) and mosquito trap counts (Figure \ref{timeseries}), though the shape of the annual trajectory differed from year to year.
The posterior distribution of the baseline mortality rate ($d_0$) had a mean of 0.88/week, roughly $60\%$ of the prior mean.
The marginal posterior means of the $\epsilon_{\nu t}$ forcing the mosquito mortality process exhibited a higher-frequency periodic oscillation (Supplementary Figure 1), although the marginal posterior distribution of each $\epsilon_{\nu t}$ overlapped zero.
In addition, the standard deviation of the mortality forcing terms was small relative to the weak prior ($E(\sigma_{\nu}|\mathbf{y}) = 0.01$, Supplemental Figure 2).
